\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}
\usepackage{multicol}
\usepackage{setspace}
\usepackage[compact]{titlesec}
\titlespacing{\section}{0pt}{0pt}{0pt}

\pagestyle{empty}

\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule] % Section formatting

\begin{document}
\setstretch{.95}
\begin{center}
  {\LARGE \textsc{\textbf{Ryan Reed Grove}}}\\

\end{center}


\begin{multicols}{2}
\hskip-.75in
\begin{tabularx}{1.5\linewidth}{>{\raggedleft\scshape}p{3cm}X}\\
  \underline{Mail:} & M-306 Martin Hall \\
          & Clemson University \\
          & Clemson, SC 29634 \\
            & \\
            \underline{Web page:} & \url{http://people.clemson.edu/~rgrove/}  \\
\end{tabularx} \\
\begin{tabularx}{1.0\linewidth}{>{\raggedleft\scshape}p{3cm}X}
\\
  \underline{Email:}   & \texttt{rgrove@clemson.edu}\\
  & \\
  \underline{Telephone:}   & \texttt{(609)-374-5724}\\
    & \\
  \underline{Citizenship:} & United States of America\\
  \\
\end{tabularx}
\end{multicols}


\section{\textbf{SKILLS, QUALIFICATIONS, AND EXPERTISE}}
\vspace*{-\baselineskip}
\vskip.23in
\begin{multicols}{2}

\hskip-1.25in
\begin{tabularx}{1.5\linewidth}{>{\raggedleft\scshape}p{3cm}X}
    &\textbf{\textit{Programming:}} \begin{itemize}
    \setlength\itemsep{.005em}
  \item C++ with MPI
  \item Python 
  \item Java 
  \item Matlab
  \item HTML
  \item R
  \item SQL
  \item C
  \item Parallel computing and multithreading
  \item Object-oriented programming

\end{itemize} \\
\\
  &\textbf{\textit{Software Packages:}}\begin{itemize}
  \setlength\itemsep{.005em}
  \item Linux and Ubuntu
  \item deal.II (finite elements)
  \item ASPECT (mantle convection)
  \item LaTeX and Beamer
  \item Girobi (linear programming)
  \item Sage
\end{itemize} \\
\end{tabularx}

\hskip-1.0in
\begin{tabularx}{1.5\linewidth}{>{\raggedleft\scshape}p{3cm}X}
  &\textbf{\textit{Computational Mathematics:}}\begin{itemize}
  \setlength\itemsep{.005em}
  \item Finite element method
  \item Stabilization schemes
  \item Viscoelastic fluid flow
  \item Navier Stokes equations
  \item Numerical linear algebra
  \item Modeling and simulation
  \item Numerical differential equations
  \item Stochastic models and processes
  \item Linear and network programming
\end{itemize} \\
\\
  &\textbf{\textit{Physics:}}\begin{itemize}
  \setlength\itemsep{.005em}
  \item Quantum mechanics
  \item Nuclear Physics
  \item Electricity and Magnetism
  \end{itemize} \\
  \\
  &\textbf{\textit{Version Control:}}\begin{itemize}
  \setlength\itemsep{.005em}
  \item GIT
  \item Subversion
\end{itemize} 
 
\end{tabularx}
\end{multicols}



\section{\textbf{EDUCATION}}
\vspace*{-\baselineskip}
\hskip-1.7in
\begin{tabularx}{1.5\linewidth}{>{\raggedleft\scshape}p{3cm}X}
  &\begin{itemize}
    \setlength\itemsep{.005em}
  \item \textbf{\textit{Ph.D., Mathematical Sciences, Clemson University}}  \hspace{37.5 mm} \textit{2017(expected)}
  
             Thesis area: Finite element method, stabilization schemes, and parallelization \textbf{QPA: 3.85/4.00}
             
\item \textbf{\textit{M.S., Applied Mathematics, Indiana University of Pennsylvania}} \hspace{14 mm} \textit{2013}
  
             Thesis area: Viscoelastic fluid flow, Navier Stokes equations \textbf{QPA: 3.83/4.00}
             
\item \textbf{\textit{B.S., Physics, Indiana University of Pennsylvania}} \hspace{40 mm}\textit{2012}
  
             Minor: Computer Science \textbf{QPA: 3.95/4.00}
             
\item \textbf{\textit{B.S., Applied Mathematics, Indiana University of Pennsylvania}} \hspace{16 mm}\textit{2012}
  
             \textbf{QPA: 3.95/4.00} 
  \end{itemize} 

\end{tabularx}


\section{\textbf{RESEARCH APPOINTMENTS}}
\vspace*{-\baselineskip}
\hskip-1.7in
\begin{tabularx}{1.5\linewidth}{>{\raggedleft\scshape}p{3cm}X}

  &\begin{itemize}
    \setlength\itemsep{.005em}
  \item \textbf{\textit{Research Assistant, Clemson University}}    \hspace{50 mm}\textit{Aug 2013 - present}
  
   Simulate problems in thermal convection using ASPECT software package.
   
	Compare nonlinear stabilization schemes for advection-diffusion equations using deal.II.        
             
\item \textbf{\textit{Web Analyst, Indiana University of Pennsylvania}} \hspace{33 mm}\textit{Sep - Dec 2012}
  
           Prepare and interpret multiple web traffic reports for the Communications Department.
           
        Find efficient ways to query and maintain a large database of web traffic information.
             
\item \textbf{\textit{ASPECT Hackathon, Texas A\&M University}} \hspace{41 mm}\textit{May 2014}
  
            Served as research and personal mentor to participants at this workshop. 
            
            Helped graduate students in the geoscientific community program in deal.II and use ASPECT.
             
  \end{itemize} 

\end{tabularx}
 
  
\section{\textbf{CONFERENCE PRESENTATIONS AND SEMINARS}}
\vskip.1in
Given over \textbf{8} contributed talks and \textbf{1} poster session at seminars and conferences. This includes:

\vspace*{-\baselineskip}
\hskip-1.7in
\begin{tabularx}{1.5\linewidth}{>{\raggedleft\scshape}p{3cm}X}

  &\begin{itemize}
    \setlength\itemsep{.005em}  
          
\item \textbf{\textit{2015 SIAM Conference on Computational Science and Engineering}} \hspace{20.5 mm}\textit{Mar 2015}
  
            The Calvin L. Rampton Salt Palace Convention Center, Salt Lake City, UT \hspace{23.5 mm} \textbf{Poster}
            
            \underline{Title:} "Comparison of Nonlinear and Linear Stabilization Schemes for Advection-Diffusion Equations"          
             
\item \textbf{\textit{Fall Southeastern Sectional Meeting of the American Mathematical Society}} \hspace{7 mm}\textit{Nov 2014}
  
           The University of North Carolina at Greensboro, Greensboro, NC  \hspace{38.5 mm} \textbf{Talk}
           
        \underline{Title:} "Comparison of Nonlinear and Linear Stabilization Schemes for Advection-Diffusion Equations"
             
  \item \textbf{\textit{Pennsylvania State System of Higher Education Mathematics Association}}    \hspace{9 mm}\textit{Apr 2013}
  
   Clarion University, Clarion, PA \hspace{91.5 mm} \textbf{Talk}
   
	\underline{Title:} "Immersed Boundary Modeling of Journal Bearings in a Viscoelastic Fluid"  
             
  \end{itemize} 

\end{tabularx}


\section{\textbf{SERVICE AND VOLUNTEER WORK}}
\vspace*{-\baselineskip}
\hskip-1.7in
\begin{tabularx}{1.5\linewidth}{>{\raggedleft\scshape}p{3cm}X}

  &\begin{itemize}
    \setlength\itemsep{.005em}
\item \textbf{\textit{SIAM Webmaster, Clemson University}} \hspace{54 mm}\textit{Aug 2014 - present }
  
    Maintainer of the website: \underline{http://people.clemson.edu/~siam/}
                       
             
\item \textbf{\textit{Volunteer Firefighter, Portage Area Fire Department}} \hspace{30 mm}\textit{Jul 2012 - May 2013}
  
   Respond to emergency calls such as QRS, fire, and hazardous materials calls.

  \item \textbf{\textit{Volunteer Assistant, Cambria Residential Services}}    \hspace{34.5 mm}\textit{Aug 2006 - Jun 2012}
  
   Take individuals with mental health disabilities into the community on social outings.
   
   Cook, clean, and transport individuals with mental health disabilities.  
             

  \end{itemize} 

\end{tabularx}





\section{\textbf{HONORS, AWARDS, AND SCHOLARSHIPS}}
\vskip.1in
Received over \textbf{\$29,000} in honors, awards, and scholarships combined.

\vspace*{-\baselineskip}
\hskip-1.7in
\begin{tabularx}{1.5\linewidth}{>{\raggedleft\scshape}p{3cm}X}

  &\begin{itemize}
    \setlength\itemsep{.005em}  
          
\item \textbf{\textit{Travel Support}} \hspace{98.5 mm}\textit{2013 - present}
  
            Received travel support for \textbf{6} conferences totalling around \textbf{\$3,000} over \textbf{2} years.
                      
          
\item \textbf{\textit{S-COAM, Indiana University of Pennsylvania}} \hspace{42 mm}\textit{2009 - 2013}
  
            Scholarship renewed \textbf{7} times totalling around \textbf{\$25,000} over \textbf{4} years.
            
            Participated in the Mathematics Enrichment Activities Network.    
             

            \item \textbf{\textit{Community Service Award}} \hspace{77 mm}\textit{2005 - 2008}
  
            Received award \textbf{3} years in a row for a total of about \textbf{\$1,000}. 
            
            Had a combined total of over \textbf{3,000} community service hours.

             
  \end{itemize} 

\end{tabularx}



\end{document}
